\documentclass{beamer}
%\usepackage{bookman} % importa a bookman family font para
%ser usado na apresentação

\title{Titulo}
\subtitle{Algum subtítulo}
\author[Marco, DKM]{Marco Henry\inst{1} \and Danilo Kotaka\inst{2}}
\institute[UEL]{Universidade Estadual De Londrina}
\date{\today}

\AtBeginSection[]
{
  \begin{frame}
    \frametitle{Sumário}
    \tableofcontents
  \end{frame}
}

\usetheme{Madrid}
%\usecolortheme{}
%\usefonttheme{structuresmallcapsserif}

\begin{document}

  \frame{\titlepage}

  \begin{frame}
    \frametitle{Titulo Slide}
    This is some text in the first slide. This is some text in the first slide. 
    This is some text in the first slide.
  \end{frame}

  \begin{frame} % frame com animacao de aparecer, um item aparece por slide
    \frametitle{Titulo Slide 2} 
    This is a text in second frame.
    For the sake of showing an example.

    \begin{itemize}
      \item<1-> Text visible on slide 1
      \item<2-> Text visible on slide 2
      \item<3> Text visible on slide 3
      \item<4-> Text visible on slide 4
      
    \end{itemize}
  \end{frame}

  \begin{frame}
    \frametitle{Teste do pause}
    In this slide \pause

    the text will be partially visible \pause

    And finally everything will be there
  \end{frame}

  \begin{frame}
    \frametitle{Teste de highlighting}

    In this slide, some important text will be \alert{highlighted} because it's important.
    Please, don't abuse it.

    \begin{block}{Remark}
      Some text 
    \end{block}

    \begin{alertblock}{Important theorem}
     Some text in red box 
    \end{alertblock}

    \begin{examples}
      Alguns textos em caixe verde. O titulo da caixa é examples 
    \end{examples}
    
  \end{frame}

  \begin{frame}
    \frametitle{Slide com 2 colunas}
    \begin{columns}
      \column{0.5\textwidth}
      This is a text in the first column
      \begin{itemize}
        \item First item
        \item Second Item
      \end{itemize}

      \column{0.5\textwidth}
      This text will be in the second column
      and on a second thoughts, this is a nice looking layout in some cases
    \end{columns}
    
  \end{frame}
  
\end{document}
